Community engagement and subgroup meta-knowledge: Some factors in the soul of a community

### 2015-08-04 PaperFinalDraft.Rnw
more ggplot2 reformatting, closes #7

<<communitysatplot, fig.cap="Responses to the question, \`\`Taking everything into account, how satisified are you with this community as a place to live?\" Communities are ordered by percentage of positive responses in 2008, making it clear the differences in distribution in 2009 and 2010.", out.width="0.99\\linewidth",fig.width = 9.5,fig.height=15,>>=
baseplot <- ggplot(mapping = aes(x=citystate, y=Freq, fill = Response, order=Response))
                   + facet_wrap(~year, nrow=3)
baseplot <- baseplot 
  + geom_bar(data = trial2$neg, stat = "identity") 
  + scale_fill_manual(breaks=c("Not at all satisfied", "2", "3", "4", "Extremely satisfied"), 
                      values=colorsB, name="Response") 
  + geom_bar(data = trial2$pos, stat = "identity")
baseplot <- baseplot 
  + coord_flip() 
  + ggtitle("Community satisfaction") 
  + xlab("") 
  +y lab("")

baseplot <- baseplot 
  + scale_y_continuous(limits=c(-0.5, 1), breaks=seq(from=-0.5, to=0.75, by=0.25), 
                       labels=c("50%", "25%", "0", "25%", "50%", "75%")) 
  + theme(legend.text=element_text(size=14), legend.title=element_text(size=16), 
          axis.text=element_text(size=14), strip.text=element_text(size=14))
baseplot 
@

@@

<<YNall, out.width="0.99\\linewidth",fig.width = 15,fig.height=9.5,fig.cap="Responses to yes/no questions about participants' behaviors, comparing all three survey years.">>=
baseplot <- ggplot(mapping = aes(Question, Freq, fill = Response) 
                   + facet_wrap(~Year)
baseplot <- baseplot 
  + geom_bar(data = trial1$neg, stat = "identity") 
  + geom_bar(data = trial1$pos, stat = "identity")
baseplot <- baseplot 
  + scale_y_continuous(breaks=seq(from=-0.75, to=0.75, by=0.25), labels=percent)

baseplot <- baseplot + coord_flip()+ xlab("")
baseplot <- baseplot 
  + scale_x_discrete(labels=rev(c("Registered to vote \n", "Voted in local election \n", "Donated money to a \n local organization", "Attended a local \n festival or event", "Gave money or food \n to an individual", "Participated in a \n church event", "Performed local \n volunteer work", "Worked with other residents \n to make change", "Attended a local \n public meeting", "Provided free shelter \n to an individual")))
baseplot <- baseplot 
  + ylab("") 
  + theme(legend.text=element_text(size=14), legend.title=element_text(size=16), 
          axis.text.y=element_text(size=20), title=element_text(size=24), 
          axis.text.x=element_text(size=14), strip.text=element_text(size=18))
baseplot
@

@@

<<YN2010plot, out.width="0.99\\linewidth",fig.width = 10, fig.height=18, fig.cap="Percentage difference from overall survey rates (2010 data). The letters A-J represent the activities listed in Figure \\ref{fig:YNall}. A: Registered to vote, B: Voted in a local election, C: Donated money to a local organization, D: Attended a local event, E: Gave money or food to an individual, F: Participated in a church event, G: Performed local volunteer work, H: Worked with other residents to make change, I: Attended a local public meeting, J: Provided free shelter to an individual.">>=
baseplot <- ggplot(dfcitiesYes) 
  + aes(Question, diff, fill = col) 
  + facet_wrap(~citystate, ncol=3) 
  + geom_bar(stat = "identity")
baseplot <- baseplot + coord_flip()

baseplot <- baseplot 
  + guides(fill=FALSE)
  + scale_y_continuous(breaks=seq(from=-.5, to=.5, by=.125),
                       labels=c("50%","", "25%","", "0","", "25%","", "50%"))
  +scale_x_discrete(labels=LETTERS[10:1])
baseplot <- baseplot 
  + ylab("") 
  + xlab("")
  + theme(axis.text.y=element_text(size=12), title=element_text(size=18), 
          axis.text.x=element_text(size=14), strip.text=element_text(size=16))
baseplot
@

>>>>

<<communitysatplot, fig.cap="Responses to the question, \`\`Taking everything into account, how satisified are you with this community as a place to live?\" Communities are ordered by percentage of positive responses in 2008, making it clear the differences in distribution in 2009 and 2010.", out.width="0.99\\linewidth",fig.width = 9.5,fig.height=15,>>=
baseplot <- ggplot(mapping = aes(x=citystate, y=Freq, fill = Response, order=Response))
  + facet_wrap(~year, nrow=3)
  + geom_bar(data = trial2$neg, stat = "identity") 
  + scale_fill_manual(breaks=c("Not at all satisfied", "2", "3", "4", "Extremely satisfied"), 
                      values=colorsB, name="Response") 
  + geom_bar(data = trial2$pos, stat = "identity") 
  + coord_flip() 
  + ggtitle("Community satisfaction") 
  + xlab("") 
  + ylab("")
  + scale_y_continuous(limits=c(-0.5, 1), breaks=seq(from=-0.5, to=0.75, by=0.25), 
                       labels=c("50%", "25%", "0", "25%", "50%", "75%")) 
  + theme(legend.text=element_text(size=14), legend.title=element_text(size=16), 
          axis.text=element_text(size=14), strip.text=element_text(size=14))
baseplot 
@

@@

<<YNall, out.width="0.99\\linewidth",fig.width = 15,fig.height=9.5,fig.cap="Responses to yes/no questions about participants' behaviors, comparing all three survey years.">>=
baseplot <- ggplot(mapping = aes(Question, Freq, fill = Response))
  + facet_wrap(~Year)
  + geom_bar(data = trial1$neg, stat = "identity") 
  + geom_bar(data = trial1$pos, stat = "identity")
  + scale_y_continuous(breaks=seq(from=-0.75, to=0.75, by=0.25), labels=percent)
  + coord_flip()+ xlab("")
  + scale_x_discrete(labels=rev(c("Registered to vote \n", "Voted in local election \n", "Donated money to a \n local organization", "Attended a local \n festival or event", "Gave money or food \n to an individual", "Participated in a \n church event", "Performed local \n volunteer work", "Worked with other residents \n to make change", "Attended a local \n public meeting", "Provided free shelter \n to an individual")))
  + ylab("") 
  + theme(legend.text=element_text(size=14), legend.title=element_text(size=16), 
          axis.text.y=element_text(size=20), title=element_text(size=24), 
          axis.text.x=element_text(size=14), strip.text=element_text(size=18))
baseplot
@

@@

<<YN2010plot, out.width="0.99\\linewidth",fig.width = 10, fig.height=18, fig.cap="Percentage difference from overall survey rates (2010 data). The letters A-J represent the activities listed in Figure \\ref{fig:YNall}. A: Registered to vote, B: Voted in a local election, C: Donated money to a local organization, D: Attended a local event, E: Gave money or food to an individual, F: Participated in a church event, G: Performed local volunteer work, H: Worked with other residents to make change, I: Attended a local public meeting, J: Provided free shelter to an individual.">>=
baseplot <- ggplot(dfcitiesYes) 
  + aes(Question, diff, fill = col) 
  + facet_wrap(~citystate, ncol=3) 
  + geom_bar(stat = "identity")
  + coord_flip()
  + guides(fill=FALSE)
  + scale_y_continuous(breaks=seq(from=-.5, to=.5, by=.125),
                       labels=c("50%","", "25%","", "0","", "25%","", "50%"))
  +scale_x_discrete(labels=LETTERS[10:1])
  + ylab("") 
  + xlab("")
  + theme(axis.text.y=element_text(size=12), title=element_text(size=18), 
          axis.text.x=element_text(size=14), strip.text=element_text(size=16))
baseplot
@
